\documentclass{article}
\usepackage{amsmath}

\title{Finite Automata}

\author{}
\date{}

\begin{document}

\maketitle

\section*{Introduction}
A finite state machine has one or more states, represented on a state-diagram as circles. As a result of an external event, the FSM can make a transition from one state to another (possibly the same) state. A transition is represented on the diagram as a directed arc, labelled with the name of the event that causes the transition to be taken. The FSM has an initial state, represented on the diagram by a lightning-trike. The current state is represented by a large dot inside the state.

\section*{Another example - text recognition}
We consider here another example, that arises in text-processing programs, such as a compiler. Suppose we wish to recognise the words "for", and float" in a stream of text. We could construct a finite state machine with the following transitions:

\begin{array}{cc}
f & o & r \\
\mathbf{f_0} & \text{start for} & \mathbf{f l o}\\
o & a & t\\
\mathbf{f l o} & \mathbf{f l o a}\\
\end{array}

Figure 4: The text recogniser

In the FSM there are states named after the partially-recognised words: $f, f o, f l, f l o,$ and floa. There are also two accepting states named $\, f o r$ and $\, f l o a t,$ shown on the diagram as double-circled states. It is obvious that for each state, there are many possible input characters that will not be recognised. For example in state $f o,$ the machine will not recognise the character $x,$ because there is no transition labelled with the event $x$ , from state $\, f o$ . If an unrecognised event occurs, the machine "dies", and ceases to process symbols -- it no longer has a current state. Effectively, the dot has been lost.

Diagrams of this kind often result from describing the behaviour of a regular expression, a topic we will deal with later.

\section*{Central concepts}
There are a number of basic concepts that are central to the study of finite automata. These concepts are:
- Alphabet (a set of symbols)
- String (a list of symbols from an alphabet)
- Language (a set of strings from the same alphabet)

\end{document}